---
title: "6_6_CV_Exercises_Review"
author: ""
date: ""
output:
  bookdown::html_document2:
    number_sections: no
    toc: true
    toc_depth: 6
    toc_float: false
    toc_collapsed: false
    self_contained: true
    lib_dir: libs
params:
  print_sol: FALSE
  hidden_notes: FALSE
---

```{r setup, include=FALSE}
library(fpp3)
```

## Exercise

For this exercise use the quarterly number of arrivals to Australia from New Zealand, 1981 Q1 – 2012 Q3, from data set `aus_arrivals`.

```{r}
# Filter data:
nzarrivals <- aus_arrivals %>% filter(Origin == "NZ")
nzarrivals
```

**a. Make a time-plot of your data. Ensure that the grid indicates at least the end of each seasonal period.**

**b. Create a training set that withholds the last two years of available data for test purposes.**

**c. Fit the following models to your training dataset and create 8-step ahead forecasts:**

**d. Which model performs better on average over all forecast horizon with this particular train-test split?**

**e. Perofrm cross-validation instead of using a single training-test set split. Do you come to the same conclusions?**
