---
title: "6_7_Exercises_MidTerm_Review"
author: ""
date: ""
output:
  bookdown::html_document2:
    number_sections: no
    toc: true
    toc_depth: 6
    toc_float: false
    toc_collapsed: false
    self_contained: true
    lib_dir: libs
params:
  print_sol: TRUE
  hidden_notes: FALSE
---

```{r setup, warning=FALSE, echo=FALSE}
library(fpp3)
```

## Exercise 1

a.  Good forecast methods should have normally distributed residuals

b.  A model with small residuals will give good forecasts

c.  The best measure of forecast accuracy is MAPE.

d.  If your model doesn't forecast well, you should make it more complicated

e.  Always choose the model with the best forecast accuracy as measured on the test set

## Exercise 2

The dataset `aus_retail` contains retail data for different australian retail industries. Specifically the industries covered are:

```{r}
aus_retail %>% distinct(Industry)
```

We are interested in the industry *Takeaway food services*.

1.  Compute the total turnover per month of all australian States combined. Plot the resulting series:

2.  Create a training withholding the last four years as a test set

3.  Obtain the optimal value of lambda suggested for a box-cox transformation. Use the whole time-series (not only the training dataset). Create a timeplot showing the result of applying that box-cox transsformation as a well as a log transformation.

4.  Fit the following models to the training dataset and forecast four years into the future with every model:

-   `decomposition_model` applying an STL decomposition and a log transformation. Use a drift model for the seasonally adjusted component and a seas. na誰ve model for the seasonal component.
-   `decomposition_model` applying an STL decomposition and a box-cox transformation with the value of lambda suggested by the guerrero feature.Use a drift model for the seasonally adjusted component and a seas. na誰ve model for the seasonal component.
-   `decomposition_model` applyting an STL decomposition with no transformation (technically incorrect since data is multiplicative). Use a drift model for the seasonally adjusted component and a seas. na誰ve model for the seasonal component.
-   `naive` model
-   `mean` model
-   `seasonal naive` model
-   `drift` model
-   `simple exponential smoothing` model

5.  Compute the accuracy metrics on:

6.  Create a timeplot of the forecasts of the best performing model in terms of `MASE`. Three figures are requested:

7.  Perform an analysis of the residuals of the model that performs best in terms of `MASE`:

## Exercise 3

`tourism` contains quarterly visitor nights (in thousands) from 1998 to 2017 for 76 regions of Australia.

```{r, include=params$print_sol}
tourism %>% distinct(Purpose)
```

1.  Extract data from the Gold Coast region using `filter()` and aggregate total overnight trips (sum over `Purpose`) using `summarise()`. Call this new dataset `gc_tourism`. Create a timeplot of `gc_tourism` as well as a correlogram.

2.  Using `slice()` or `filter()`, create three training sets for this data excluding the last 1, 2 and 3 years.

3.  Compute **one year** forecasts for each training set using the seasonal na誰ve method (`SNAIVE()`). Call these `gc_fc_1`, `gc_fc_2` and `gc_fc_3`, respectively. Generate one year forecasts for each model. Create a single timeplot with the time series (train+test sets) and the forecasts produced by the three models

4.  Use `accuracy()` to compare the test set forecast accuracy(). Compute the accuracy on both the train and test datasets:

-   Accuracy metrics based on the training dataset (on the residuals):

-   Accuracy metrics based on the test dataset (forecast errors)

5.  What would you do to assess the performance of the model in a more statitically robust manner?
