---
title: "Efficient Market Hypothesis (Group assignment)"
author: "Juan Garbayo - Time Series Analysis"
date: "4/8/2022"
output:
  bookdown::html_document2:
    number_sections: no
    toc: true
    toc_depth: 6
    toc_float: false
    toc_collapsed: false
    self_contained: true
    lib_dir: libs
params:
  run_snippet: FALSE
  print_sol: FALSE
  hidden_notes: FALSE
---

```{r}
library(fpp3)
library(patchwork)
```

# References

[1] Fama, Eugene (1970). "Efficient Capital Markets: A Review of Theory and Empirical Work". Journal of Finance. 25 (2): 383–417. doi:10.2307/2325486. JSTOR 2325486.

[2] Investopedia - Efficient Market Hypothesis [Link](https://www.investopedia.com/terms/e/efficientmarkethypothesis.asp)

# The Efficient Market Hypothesis

The goal of this assignment is to compare a prediction strategy based on the Efficiet Market Hypothesis (EMH) with the first of the non-trivial models you will work with: exponential smoothing.

Essentially, the EMH states that stocks are accurately priced and reflect all available information. This makes it impossible to consistently beat the market by analysis.

In his influential 1970 paper ([1]), Eugene Fama proposes three categories of efficiency that differ in the information considered reflected in the prices:

1. *Weak-form of the EMH*: considers information contained in historical prices.
2. *Semi-strong form of EMH*: considers information publicly available beyond historical prices.
3. *Strong-form*: considers private (privileged) information.

Here we are going to consider the weak-form of the EMH and work only with the information contained in historical prices.

# Assignment

The assignment consists in:

### **1. Download historical data from a Stock Market Index and generate a dataset with that data.** (0.5 point)

The idea is that you **download the data using the separate notebook provided**, **store it as a .csv** and **import it here.** You will work with two datasets:

  * **Financial Times Stock Exchange:** tracks the 100 companies with the largest market capitalization on the London Stock Exchange.
  
The date ranges to be used are:

  * **Initial date**: 7-th of May 2017
  * **Final date**: the current date.
  
**Your final dataset must be an object of type `tsibble` with the following characteristics**:

* key = symbol
* index = trading_day

```{r}
```

### **1.1 Create a time-plot of your data and briefly describe it (max 75 words)** (0.5 points)

```{r}

```

### **2. Create three training datasets containing 80, 60 and 40% of your data** (0.5 points)

```{r}

```

### **3. Fit both a Naïve model and a Simple Exponential Smooting model to each of these training datasets** (0.5 points)

```{r}

```

### **4. Generate forecasts of 5 trading days for each of the trained models** (1 point)

The result of this step should be a `fable` or forecast table. Name it `fc`

Add a column `h` to `fc` indicating the forecast horizont of each forecast.

* After adding that column, apply the following command: `as_fable(response = "close", distribution = close)`. This is to ensure that the output after performing these operations is still a fable.

```{r}

```
### **5. For each combination of model, training dataset and forecast horizon compute the RMSE, MAE and MAPE. Store the result in a variable called `summary`** (1 point)

```{r}

```
### **6. Use facet wrap to produce 3 graphs, one for each of the three error metrics used** (2 points)

The graphs should depict the RMSE for each forecast horizon and for each combination of model and training dataset.

* Does the training dataset have an effect on the errors?
* Does one of the models outperform the other?

```{r}

```

### **7. Evaluate the same metrics on the same models, but this time using cross validation** (2 points)

The end-goal is that you produce the same final graph (facet_wrap graph on the error metrics), but this time only two lines per graph should be depicted (one line per model).

The smallest training dataset shall contain 40% of the trading days. The trading datasets shall increase in steps of 1 trading day. You may later repeat this for .steps of 5 and note the difference in running time.

```{r}

```

### **8. Present your conclusions** (1.5 points)
