---
title: "ZZ_StockPrices"
author: "Juan Garbayo"
date: 
output: 
  html_document:
    toc: true
    toc_depth: 6
    self_contained: true
---

# References

1. Quantmod - [Link](https://www.quantmod.com/)
2. Tidyquant - [Link](https://business-science.github.io/tidyquant/)
3. Yahoo finance - Symbol search - [Link](https://finance.yahoo.com/lookup)

# Introduction

The `tidyquant` libary is essentially a wrapper to various `xts`, `zoo`, `quantmod`, `TTR` and `PerformanceAnaytics` package functions that integrates these with the tidy `tibble` format.

It enables to use quantitative functions with the `tidyverse` functions and data structures. 

See reference 2 for more information, documentation and examples.

# Install and load packages

```{r, eval=FALSE}
install.packages("tidyquant")
```

```{r, error=FALSE, warning=FALSE, message = FALSE}
library(tidyquant)
library(tidyverse)
library(feasts)
```

# Downloading prices and generating the tsibble

Have a look at the list of symbols on reference 3.

```{r}
# 1. Select the asset you want to download
# NOTE: check reference 3 to find the appropriate symbol for the asset.

symbol = "^GSPC" # Example corresponding to S&P500

# 2 Select start and end date for the analysis.
start_date = "2017-05-01"
end_date = as.Date(now())

# 3. Download requested data
prices <- tq_get(x = symbol,
                 from = start_date,
                 to = end_date,
                 get = "stock.prices")

# 4. Inspect results
bind_rows(head(prices, 5), tail(prices, 5))
```

Once the data has been downloaded, we now proceed to convert it to a tsibble

```{r}
# Process tibble to generate a tsibble
prices <- prices %>%

  # 1. Generate new index
  mutate(trading_day = row_number()) %>%
  
  # 2. Select variables of interest
  select(symbol, trading_day, date, close) %>%
   
  # 3. Convert to tsibble
  as_tsibble(index = trading_day, regular = TRUE)

# 4. Inspect results
bind_rows(head(prices, 5), tail(prices, 5))
```

```{r}
autoplot(prices)
```

```{r}
write_csv(prices, "SP500_Prices.csv")
```

# Analysis

1. Compute the first order difference in closing prices and judge whether or not the series (see asynchronous session - stock prices exercise).

* Does it have a trend?
* Is similar to white noise?
